Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
List looks good.

There are many reasons why this lack of both software citations in general and
standard practices for software citation are of concern: \katznote{Are there any more
items that should be added to this list?}

>>>>

There are many reasons why this lack of both software citations in general and
standard practices for software citation are of concern:
